Machine learning methods in streamflow prediction considering climate variable windowing

### 2021-06-28 paper/paper.tex
Pequena correção em um parágrafo
Melhora no posicionamento dos caption dos gráficos de importância
Label nas seções

\section{Introduction}

@@

In Section 2, the related bibliography regarding machine learning models in the context of streamflow prediction is introduced. The study area and data used for the modeling are presented in Section 3, while the pre-processing data and results are described in Section 4, followed by a analysis about the results in Section 5 and conclusion in Section 6.

\section{Related bibliography}

@@

\section{Material and methods}

@@

\subsection{Study area and descriptive analysis}
We chose Três Marias reservoir for two main reasons. First because of its importance to the Brazilian electricity system, since this reservoir holds a hydropower plant of 396 MW of installed capacity. Second, there are available atmospheric climate data at a high spatial resolution (5 km) for the Southeastern region, where Três Marias is located. Três Marias reservoir is inside the Alto São Francisco sub-basin in Minas Gerais state (Figure \ref{fig:studyarea}). We defined the river-group of each coordinate point using as reference \cite{fundep}.

@@

\subsection{Data}

@@

\subsection{Methods and evaluation criteria}

@@

\begin{figure}[htbp]
    \centering
  %   \includegraphics[width=1\linewidth]{Diagrams/Pipelines.PNG}
    {\small\includesvg[width=.8\linewidth]{Diagrams/gridsearch.drawio}}
    \caption{Pipeline setup for machine learning model search}
    \label{fig:pipelines}
  \end{figure}

@@

\section{Data preprocessing}

@@

\subsection{Data reduction and integration}

@@

\section{Results and discussion}

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{.49\textwidth}
        \centering
        \includesvg{Graphs/CategorizedImportance_w01}
        \captionsetup{margin={.15\textwidth, 0cm}}
        \caption{1 day windowing}
        \label{fig:CategorizedImportance01}
    \end{subfigure}
    \begin{subfigure}[b]{.49\textwidth}
        \centering
        \includesvg{Graphs/CategorizedImportance_w15}
        \captionsetup{margin={.15\textwidth, 0cm}}
        \caption{15 days windowing}
        \label{fig:CategorizedImportance02}
    \end{subfigure}
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includesvg{Graphs/CategorizedImportance_w30}
        \captionsetup{margin={.23\linewidth, 0cm}}
        \captionsetup{justification=justified,singlelinecheck=false}
        \caption{30 days windowing}
        \label{fig:CategorizedImportance03}
    \end{subfigure}
    \caption{Variable importance for \subref{fig:CategorizedImportance01} 1, \subref{fig:CategorizedImportance02} 15, and \subref{fig:CategorizedImportance03} 30 days windowing}
    \label{fig:CategorizedImportance}
\end{figure}

@@

\section{Conclusion}

>>>>

\section{Introduction}
\label{sec:Introduction}

@@

In Section \ref{sec:RelatedBibliography}, the related bibliography regarding machine learning models in the context of streamflow prediction is introduced. The study area and data used for the modeling are presented in Section \ref{ssec:StudyAreaDecriptiveAnalysis}, while the pre-processing data and results are described in Section \ref{sec:DataPreprocessing}, followed by a analysis about the results in Section \ref{sec:ResultsDiscussion} and conclusion in Section \ref{sec:Conclusion}.

\section{Related bibliography}
\label{sec:RelatedBibliography}

@@

\section{Material and methods}
\label{sec:MateriaMethods}

@@

\subsection{Study area and descriptive analysis}
\label{ssec:StudyAreaDecriptiveAnalysis}

We chose Três Marias reservoir for two main reasons. First because of its importance to the Brazilian electricity system, since this reservoir holds a hydropower plant of 396 MW of installed capacity. Second, there are available atmospheric climate data at a high spatial resolution (5 km) for the Southeastern region, where Três Marias is located. Três Marias reservoir is inside the Alto São Francisco sub-basin in Minas Gerais state (Figure \ref{fig:studyarea}). We defined the river-group of each coordinate point using as reference \cite{fundep}.

@@

\subsection{Data}
\label{ssec:Data}

@@

\subsection{Methods and evaluation criteria}
\label{ssec:MethodsEvaluation}

@@

\begin{figure}[htbp]
    \centering
    {\footnotesize\includesvg[width=.8\linewidth]{Diagrams/gridsearch.drawio}}
    \caption{Pipeline setup for machine learning model search}
    \label{fig:pipelines}
\end{figure}

@@

\section{Data preprocessing}
\label{sec:DataPreprocessing}

@@

\subsection{Data reduction and integration}
\label{ssec:DataReductionIntegration}

@@

\section{Results and discussion}
\label{sec:ResultsDiscussion}

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{.49\textwidth}
        \centering
        \includesvg{Graphs/CategorizedImportance_w01}
        \captionsetup{margin={.17\textwidth, 0cm}}
        \caption{1 day windowing}
        \label{fig:CategorizedImportance01}
    \end{subfigure}
    \begin{subfigure}[b]{.49\textwidth}
        \centering
        \includesvg{Graphs/CategorizedImportance_w15}
        \captionsetup{margin={.17\textwidth, 0cm}}
        \caption{15 days windowing}
        \label{fig:CategorizedImportance02}
    \end{subfigure}
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includesvg{Graphs/CategorizedImportance_w30}
        \captionsetup{margin={.26\linewidth, 0cm}}
        \captionsetup{justification=justified,singlelinecheck=false}
        \caption{30 days windowing}
        \label{fig:CategorizedImportance03}
    \end{subfigure}
    \caption{Variable importance for \subref{fig:CategorizedImportance01} 1, \subref{fig:CategorizedImportance02} 15, and \subref{fig:CategorizedImportance03} 30 days windowing}
    \label{fig:CategorizedImportance}
\end{figure}

@@

\section{Conclusion}
\label{sec:Conclusion}
